Performance of two different ontological and data access methods

### 2014-07-08 cold2014/magnus.tex
smaller changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@744 43ef1190-90fd-4dd7-a769-d0121f02b80e

We will also show how to create a viable web application which
utilizes such complex data, mainly for the purpose of conducting
performance tests to determine the weaknesses of each approach. This
will be done with complex data found on the web today from different
car manufacturers.  With performance we mean the response time between
a HTTP post operation against the application and when
the application presents the user with an answer. The application will
contain the possibility to do HTTP posts against both approaches.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself important, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

@@

\subsection{Full factorial experiment}
A full factorial experiment is when one got $k$ factors and $n$ amount
of levels. This means that there is $n^k$ \emph{factorial designs}
which result in $n^k$ designs to execute.  We have chosen only
two-level experiments for this research, but the factors may
vary. This means that we will use a $2^k$ full factorial design for
every experiment. The experiments consist of $2^k$ combinations with
$k$ factors. This results in a \emph{planning matrix} that shows the
actual runs in the experiment.

\subsection{Running the experiments}
In this section we will present several experiments with different
number of factors.  The objective is to find out how the two approaches
will perform in comparison and identifying which factors affect the
outcome of each experiment. Although the ontology is not the
only issue that distinguishes these approaches, it is the key feature,
and therefore, we will shall refer to that as a factor.

In the experiments the definition for VSO/COO is \textsf{-vso} and for
CO is \textsf{-co}.  These two definitions stand for which ontology
are tested in a particular run. In practice this means that when we
send in the keyword \textsf{-vso} we only run the specification search
against the car models represented by VSO/COO, in our case the data
from Daimler. This is referred to as the ontology factor in each
experiment and is a factor in all the experiments which are presented
in this paper. The ontology factor represents the difference in how
the data are represented and how the ontologies are structures, and
with this factor we want to determine how this affects the overall
performance.  We have programmed the application so that the querying
of the ontologies are done as similar as possible on both levels. This
was done to eliminate any interference from the application.

@@

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot}. This method assumes that the
estimated effects are normally distributed with means equal to the
effects. The means of all estimated effects are zero. Resulting in a
plot where the estimated effect would end up on a straight line. This
plot is then testing whether all the estimated effects have the same
distribution. All deviations of the straight line indicates a
significant factor. In our results we have used the absolute value of
the effects, also called a half-normal plot. The advantages of using
the half-normal plot is that all large estimated effects will end up
in the top right corner. This means that the highest performance
significance will end up in the top right corner. The
axes themselves are not important to understand the plot nor the
results, refer to \cite{PlanExp} for details.
We have also set  the significance level at $\alpha =
0.05$, where \textsf{DanielPlot} is using Lenth's method for the
analysis of unreplicated factorials.

>>>>

We have created a web application prototype which uses such complex
data, mainly for the purpose of conducting performance tests to
determine the weaknesses of each approach. This will be done with
complex data found on the web today from different car manufacturers.
With performance we mean the response time between a HTTP post
operation against the application and when the application presents
the user with an answer. The application will contain the possibility
to do HTTP posts against both approaches.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself important, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using Semantic Web technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

@@

\subsection{Full factorial experiment}
A full factorial experiment is when one got $k$ factors and the number
of levels is $n$. This means that there is $n^k$ \emph{factorial designs}
which result in $n^k$ designs to execute.  We have chosen only
two-level experiments for this research, but the factors may
vary. This means that we will use a $2^k$ full factorial design for
every experiment. The experiments consist of $2^k$ combinations with
$k$ factors. This results in a \emph{planning matrix} that shows the
actual runs in the experiment.

\subsection{Running the experiments}
In this section we will present several experiments with different
number of factors.  The objective is to find out how the two approaches
will perform in comparison and identifying which factors affect the
outcome of each experiment.

In the experiments the definition for VSO/COO is \textsf{-vso} and for
CO is \textsf{-co}.  These two definitions stand for which ontology
are tested in a particular run. In practice this means that when we
send in the keyword \textsf{-vso} we only run the specification search
against the car models represented by VSO/COO, in our case the data
from Daimler. This is referred to as the ontology factor in each
experiment, and is a factor in all the experiments which are presented
in this paper. The ontology factor represents the difference in how
the data are represented and how the ontologies are structures, and
with this factor we want to determine how this affects the overall
performance.  We have programmed the application so that the querying
of the ontologies are done as similar as possible on both levels. This
was done to eliminate any interference from the application.

@@

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot}. This method assumes that the % TODO: Dette må forbedres
estimated effects are normally distributed with means equal to the
effects. The means of all estimated effects are zero. Resulting in a
plot where the estimated effect would end up on a straight line. This
plot is then testing whether all the estimated effects have the same
distribution. All deviations of the straight line indicates a
significant factor. In our results we have used the absolute value of
the effects, also called a half-normal plot. The advantages of using
the half-normal plot is that all large estimated effects will end up
in the top right corner. This means that the highest performance
significance will end up in the top right corner. The
axes themselves are not important to understand the plot nor the
results, refer to \cite{PlanExp} for details.
We have also set  the significance level at $\alpha =
0.05$, where \textsf{DanielPlot} is using Lenth's method for the
analysis of unreplicated factorials.
